---
title: "Untitled"
output:
  html_document: default
  pdf_document: default
  word_document: default
date: "2025-08-21"
---
---
title: "Thesis Simulation Part"
output: html_document
date: "2025-08-20"
---
---
title: "My Document"
output: html_document
---

```{r setup, include= FALSE}
# Set global chunk options
knitr::opts_chunk$set(
	echo = FALSE,
	error = TRUE,
	message = TRUE,
	warning = TRUE,
	results = "markup"
)
```
### Introduction 

My Thesis "Difference-in-Difference with multiple time periods" is trying to tackle the problems with DiD method related to multiple time periods. 
DiD method involves comparing the change in outcomes between a treatment group and a control group, both before and after the intervention.
DiD relies on few assumption: parallel trend, no anticipation, SUTVA, no spilover effect.
DID is often implemented using a Two-way fixed effects (TWFE) (unit-specific & time-specific fixed effects) model, where the treatment variable is interacted with a time dummy variable. In the canonical DiD 2x2, TWFE is proved to work perfectly.
The problems raise when DiD is implemented in multiple time periods, TWFE is proved to be biased in some settings (goodman-bacon 2020). Researchers have to find better ways to tackle this problem. There have been few papers publishing in last several years. Among them, 2 methods are becoming popular: CS & SA.

This Thesis Simulation Part is trying to show two things:
1. Which settings the TWFE works well and which settings doesn't
2. How CS & SA method perform in the setting where TWFE method fails.

### Part 1: TWFE
## 1.1 Settings where TWFE performance great
TWFE works well in setting when there is no staggered adoption, or staggered adoption with homogenenous treatment effect. 
Although, it could be proved by math, I would like to prove it via simulation.
I make 3 DGPs for 3 cases: 
1. not staggered adoption with homogenous treatment effect.
2. not staggered adoption with dynamic treatment effect.
3. staggered adoption with the same homogenenous treatment effect tau. 

in each case, I would like to generate a balanced panel dataset with 600 units over the time periods T = 36 years, from 1990 to 2025. These 600 units have both time-varying year effects and time-invariant unit effects (which in the data are independently drawn from N(0,0.5^2)). These units are also incorporated in one of 30 randomly drawn groups, which differ in terms of whether and when treatment was initiated. 

I believe this simulated dataset could be seen in the real-world (for example: 600 firms, assigned randomly in 30 states applying minimum wage policy in different year betwween 1990-2025). 
I assume the treatment effect once turn on, never turn off.
I also use monte carlo simulation to check the robustness of the results. 


```{r library}

library(tidyverse)
library(patchwork)
library(kableExtra)
library(lfe)
library(lmtest)
library(xtable)
library(did)
library(magrittr)
library(ggthemes)
library(bacondecomp)
library(multcomp)
library(fastDummies)
library(ggforce)
# set plot features
select <- dplyr::select
theme_set(theme_clean() + theme(plot.background = element_blank(),
                                legend.background = element_blank()))
set.seed(42)

```
#1.1.1 Create DGP1: one treatment period, homogenenous treatment effect
Assume we have 600 firms, randomly assigned to 30 states. 30 states seperated into 2 groups: group 1 (control - C), group 2 (treated - T).group 2 initiate treatment at t= 2008. we set true homogeneous TE constant and equal 2. 
600 firms have unit-fe ~ N(0,0.5^2) & time-TE is yearly-TE ~ N(2, 0.2^2). 
```{r data1}
# Data 1 - One Treatment Period, Homogeneous Treatment Effects --------------
make_data1 <- function(...) {
  
  # Fixed Effects ------------------------------------------------
  # unit fixed effects
  unit <- tibble(
    unit = 1:600, 
    unit_fe = rnorm(600, 0, 0.5),
    # generate state
    state = sample(rep(1:30, 20), 600, replace = FALSE),
    # generate treatment groups
    group = case_when(
      state %in% 1:15 ~ 1,
      state %in% 16:30 ~ 2
    ),
    evertreated = ifelse(group == 2, "T", "C"),
    # avg yearly treatment effects by group
    hat_gamma = case_when(
      group == 2 ~ 2,
      TRUE ~ 0
    )) %>%
    # generate unit specific yearly treatment effects 
    rowwise() %>% 
    mutate(gamma = ifelse(group == 2, rnorm(1, hat_gamma, .2), 0)) %>% 
    ungroup()
  
  # year fixed effects 
  year <- tibble(
    year = 1990:2025,
    year_fe = rnorm(36, 0, 0.5))
  
  # full interaction of unit X year 
  crossing(unit, year) %>% 
    # make error term and get treatment indicators and treatment effects
    mutate(error = rnorm(nrow(.), 0, 0.5),
           treat = ifelse(evertreated == "T" & year >= 2008, 1, 0),
           tau = ifelse(treat == 1, gamma, 0)) %>%
    # calculate the dep variable
    mutate(dep_var = unit_fe + year_fe + tau + error)
}

# make data
data1 <- make_data1()
head(data1)
```
# Create plot for DGP 1
```{r plot1}
knitr::opts_chunk$set(echo = TRUE)
plot1 <- data1 %>% 
  ggplot(aes(x = year, y = dep_var, group = unit)) +
  # unit specific lines
  geom_line(alpha = 1/10, color = "grey") + 
  # group specific averages
  geom_line(
    data = . %>% 
      group_by(evertreated, year) %>% 
      summarize(dep_var = mean(dep_var)),
    aes(x = year, y = dep_var, group = factor(evertreated),
        color = factor(evertreated)), size = 1) + 
  labs(x = "", y = "Value", color = "Group") + 
  geom_vline(xintercept = 2007.5, color = '#4B5F6C',
             linetype = "dashed", size = 1) + 
  scale_color_manual(values = c("#A7473A", "#4B5F6C")) + 
  ggtitle("Simulation 1") + 
  labs(subtitle = expression(paste("Not Staggered + Homogenous TE ", tau))) + 
  theme(legend.position = 'bottom',
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5, vjust = 0.5, angle = 360))
plot1
```
do 500 simulations, estimate ATT and plot for DGP1
we run TWFE with monte carlo simulation 500 times. Extract 'estimate' and plot it with true TE tau = 2.
```{r sim1, include=TRUE}
# make function to do this by data type 
dosims <- function(i, fun) {
  # make data from function
  dt <- fun()
  # estimate model and take what you need
  felm(dep_var ~ treat | unit + year | 0 | state, data = dt) %>% 
    broom::tidy(conf.int = TRUE) %>% 
    dplyr::select(estimate) %>% 
    dplyr::mutate(sim = i)
}

# estimate over the dataset 500 sims
simdata1 <- map_dfr(1:500, .f = dosims, fun = make_data1)
# make plots
tau1 <- 2
plot2 <- simdata1 %>% 
  ggplot(aes(x = estimate)) + 
  geom_density(fill = "#377EB8", alpha = 1/5) + 
  geom_vline(xintercept = tau1, linetype = "dashed", color = "#E41A1C", size = 1) + 
  ggtitle("Simulation 1") + 
  labs(subtitle = expression(paste("Not Staggered + Homogeneous TE ", tau))) +
  labs(x = "", y = "Density") + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5, vjust = 0.5, angle = 360))
plot2
```
#1.1.2. Create DGP2: one treatment period, dynamic treatment effect.
Similar to DGP1, 600 firms ~ N(0, 0.5^2), 30 states, 2 groups: Treated- Control. treated at t = 2008. However, the yearly-TE now is vary over time (dynamic TE).  inititated yearly-TE of firm i in treated group gamma ~ N(0.3, 0.2^2) & over n year, the yearly-TE grow gamma*n (n= t-2008)
```{r data2, include= TRUE}
# Data 2 - One Treatment Period, Dynamic Treatment Effects --------------

make_data2 <- function(...) {
  
  # Fixed Effects ------------------------------------------------
  # unit fixed effects
  unit <- tibble(
    unit = 1:600, 
    unit_fe = rnorm(600, 0, 0.5),
    # generate state
    state = sample(rep(1:30, 20), 600, replace = FALSE),
    # generate treatment groups
    group = case_when(
      state %in% 1:15 ~ 1,
      state %in% 16:30 ~ 2
    ),
    evertreated = ifelse(group == 2, "T", "C"),
    # avg yearly treatment effects by group
    hat_gamma = case_when(
      group == 2 ~ .3,
      TRUE ~ 0
    )) %>%
    # generate unit specific yearly treatment effects 
    rowwise() %>% 
    mutate(gamma = rnorm(1, hat_gamma, .2), 0) %>% 
    ungroup()
  
  # year fixed effects 
  year <- tibble(
    year = 1990:2025,
    year_fe = rnorm(36, 0, 0.5))
  
  # full interaction of unit X year 
  crossing(unit, year) %>% 
    # make error term and get treatment indicators and treatment effects
    mutate(error = rnorm(nrow(.), 0, 0.5),
           treat = ifelse(evertreated == "T" & year >= 2008, 1, 0),
           tau = ifelse(treat == 1, gamma, 0)) %>%
    # calculate the dep variable
    group_by(unit) %>% 
    mutate(cumtau = cumsum(tau)) %>% 
    mutate(dep_var = unit_fe + year_fe + cumtau + error)
}

# make data
data2 <- make_data2()
```
DGP2 plot
```{r plot2, include=TRUE}
plot3 <- data2 %>% 
  ggplot(aes(x = year, y = dep_var, group = unit)) +
  # unit specific lines
  geom_line(alpha = 1/10, color = "grey") + 
  # group specific averages
  geom_line(
    data = . %>% 
      group_by(evertreated, year) %>% 
      summarize(dep_var = mean(dep_var)),
    aes(x = year, y = dep_var, group = factor(evertreated),
        color = factor(evertreated)), size = 1) + 
  labs(x = "", y = "", color = "Group") + 
  ylim(c(0-5, 10)) + 
  geom_vline(xintercept = 2007.5, color = '#4B5F6C',
             linetype = "dashed", size = 1) + 
  scale_color_manual(values = c("#A7473A", "#4B5F6C")) + 
  ggtitle("Simulation 2") + 
  labs(subtitle = expression(paste("Not Staggered + Dynamic ", tau))) + 
  theme(legend.position = 'bottom',
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5, vjust = 0.5, angle = 360))
plot3
```
do 500 simulations, estimate ATT and plot for DGP2
in this setting, 
true TE tau = average of all these over 18 years treatmentperiod (2008-2025).
= (0.3 + 0.6 + 0.9+...+5.4)/18 = 2.85
```{r sim2}
# estimate over the dataset 500 sims
simdata2 <- map_dfr(1:500, .f = dosims, fun = make_data2)
# make plots
tau2 <- mean(cumsum(rep(0.3, length(2008:2025))))
plot4 <- simdata2 %>% 
  ggplot(aes(x = estimate)) + 
  geom_density(fill = "#377EB8", alpha = 1/5) + 
  geom_vline(xintercept = tau2, linetype = "dashed", color = "#E41A1C", size = 1) + 
  ggtitle("Simulation 2") + 
  labs(subtitle = expression(paste("Not Staggered + Dynamic ", tau))) +
  labs(y = "", x = expression(widehat(delta^'DD'))) + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
plot4
```
#1.1.3 Create DGP3: staggered adoption + homogeneous TE
To creat staggered adoption, homogenous TE, I assign 600 units, 30 states into 3 groups: group 1 got treated in 1999, group 2 got treated in 2008, group 3 got treated in 2017. no never-treated group. All 3 groups have average yearly TE equal to 3 (constant)  since they got treated. 

```{r data3, include= TRUE}
# Data 3 - Multiple Treatment Periods and Constant Equal Treatment Effects --------------
make_data3 <- function(...) {
  
  # Fixed Effects ------------------------------------------------
  # unit fixed effects
  unit <- tibble(
    unit = 1:600, 
    unit_fe = rnorm(600, 0, 0.5),
    # generate state
    state = sample(rep(1:30, 20), 600, replace = FALSE),
    # generate treatment groups
    group = case_when(
      state %in% 1:10 ~ 1999,
      state %in% 11:20 ~ 2008,
      state %in% 21:30 ~ 2017
    ),
    # avg yearly treatment effects by group
    hat_gamma = case_when(
      group == 1999 ~ 3,
      group == 2008 ~ 3,
      group == 2017 ~ 3
    )) %>%
    # generate unit specific yearly treatment effects 
    rowwise() %>% 
    mutate(gamma = rnorm(1, hat_gamma, .2), 0) %>% 
    ungroup()
  
  # year fixed effects 
  year <- tibble(
    year = 1990:2025,
    year_fe = rnorm(36, 0, 0.5))
  
  # full interaction of unit X year 
  crossing(unit, year) %>% 
    # make error term and get treatment indicators and treatment effects
    mutate(error = rnorm(nrow(.), 0, 0.5),
           treat = ifelse(year >= group, 1, 0),
           tau = ifelse(treat == 1, gamma, 0)) %>%
    # calculate the dep variable
    mutate(dep_var = unit_fe + year_fe + tau + error)
}

# make data
data3 <- make_data3()
```
#plot for DGP 3
```{r plot3, include = TRUE}
plot5 <- data3 %>% 
  ggplot(aes(x = year, y = dep_var, group = unit)) +
  # unit specific lines
  geom_line(alpha = 1/10, color = "grey") + 
  # group specific averages
  geom_line(
    data = . %>% 
      group_by(group, year) %>% 
      summarize(dep_var = mean(dep_var)),
    aes(x = year, y = dep_var, group = factor(group),
        color = factor(group)), size = 1) + 
  labs(x = "", y = "", color = "Group") + 
  geom_vline(xintercept = 1998.5, color = "#A7473A",
             linetype = "dashed", size = 1) + 
  geom_vline(xintercept = 2007.5, color = "#4B5F6C", 
             linetype = "dashed", size = 1) + 
  geom_vline(xintercept = 2016.5, color = "#51806a", 
             linetype = "dashed", size = 1) + 
  scale_color_manual(values = c("#A7473A", "#4B5F6C", "#51806a")) + 
  ggtitle("Simulation 3") + 
  labs(subtitle = expression(paste("Staggered + Homogeneous TE ", tau))) + 
  theme(legend.position = 'bottom',
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5), 
        plot.subtitle = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5, vjust = 0.5, angle = 360))
plot5
```
do 500 simulations, estimate ATT and plot for DGP3
in this setting, true tau = 3
```{r sim3, include = TRUE}
# estimate over the dataset 500 sims
# dosims already above
simdata3 <- map_dfr(1:500, .f = dosims, fun = make_data3)
# make plots
tau3 <- 3
plot6 <- simdata3 %>% 
  ggplot(aes(x = estimate)) + 
  geom_density(fill = "#377EB8", alpha = 1/5) + 
  geom_vline(xintercept = tau3, linetype = "dashed", color = "#E41A1C", size = 1) + 
  #geom_vline(xintercept = 0, linetype = "dashed", color = "black", size = 1) + 
  ggtitle("Simulation 3") + 
  labs(subtitle = expression(paste("Staggered + Homogenous TE ", tau))) +
  labs(x = "", y = "") + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
plot6
```
#1.1.4 Plot for 1.1
```{r plot135,include= TRUE}
plot_dgp_123 <- plot1 + plot3 + plot5
plot_dgp_123
```

```{r plot246, include = TRUE}
plot_TWFE_work <- plot2 + plot4 + plot6
plot_TWFE_work
```
##1.2: settings where TWFE perform poorly
TWFE is proved to work poorly in staggered adoption with heterogeneous TE.
I generate 3 different dataset to prove it. 
the setting is similar. 600 units, 30 states, 3 groups ~ 3 treatment periods. no never-treated group. 
#1.2.1: Create DGP4: staggered adoption, constant different treatment
similar to DGP3, I just change the average TE by group gamma: for group 1999, 6; for group 2008, 3; for group 2017, 1.
```{r data4, include= TRUE}
# Data 4 - Multiple Treatment Periods and Constant Different Treatment Effects --------------
make_data4 <- function(...) {
  
  # Fixed Effects ------------------------------------------------
  # unit fixed effects
  unit <- tibble(
    unit = 1:600, 
    unit_fe = rnorm(600, 0, 0.5),
    # generate state
    state = sample(rep(1:30, 20), 600, replace = FALSE),
    # generate treatment groups
    group = case_when(
      state %in% 1:10~ 1999,
      state %in% 11:20 ~ 2008,
      state %in% 21:30 ~ 2017
    ),
    # avg yearly treatment effects by group
    hat_gamma = case_when(
      group == 1999 ~ 6,
      group == 2008 ~ 3,
      group == 2017 ~ 1
    )) %>%
    # generate unit specific yearly treatment effects 
    rowwise() %>% 
    mutate(gamma = rnorm(1, hat_gamma, .2), 0) %>% 
    ungroup()
  
  # year fixed effects 
  year <- tibble(
    year = 1990:2025,
    year_fe = rnorm(36, 0, 0.5))
  
  # full interaction of unit X year 
  crossing(unit, year) %>% 
    # make error term and get treatment indicators and treatment effects
    mutate(error = rnorm(nrow(.), 0, 0.5),
           treat = ifelse(year >= group, 1, 0),
           tau = ifelse(treat == 1, gamma, 0)) %>%
    # calculate the dep variable
    mutate(dep_var = unit_fe + year_fe + tau + error)
}

# make data
data4 <- make_data4()
```
plot
```{r plot4, include = TRUE}
# plot
plot7 <- data4 %>% 
  ggplot(aes(x = year, y = dep_var, group = unit)) +
  # unit specific lines
  geom_line(alpha = 1/10, color = "grey") + 
  # group specific averages
  geom_line(
    data = . %>% 
      group_by(group, year) %>% 
      summarize(dep_var = mean(dep_var)),
    aes(x = year, y = dep_var, group = factor(group),
        color = factor(group)), size = 1) + 
  labs(x = "", y = "Value", color = "Group") + 
  geom_vline(xintercept = 1998.5, color = "#A7473A",
             linetype = "dashed", size = 1) + 
  geom_vline(xintercept = 2007.5, color = "#4B5F6C" , 
             linetype = "dashed", size = 1) + 
  geom_vline(xintercept = 2016.5, color = "#51806a" , 
             linetype = "dashed", size = 1) + 
  scale_color_manual(values = c("#A7473A", "#4B5F6C", "#51806a")) + 
  ggtitle("Simulation 4") + 
  labs(subtitle = expression(paste("Staggered + Constant/Unequal ", tau))) + 
  theme(legend.position = 'bottom',
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5), 
        plot.subtitle = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5, vjust = 0.5, angle = 360))
plot7
```
```{r sim4, include= TRUE}
# do simulations, estimate ATT and plot ---------------------------------
# make function to do this by data type 
dosims <- function(i, fun) {
  # make data from function
  dt <- fun()
  # estimate model and take what you need
  felm(dep_var ~ treat | unit + year | 0 | state, data = dt) %>% 
    broom::tidy(conf.int = TRUE) %>% 
    dplyr::select(estimate) %>% 
    dplyr::mutate(sim = i)
}

# estimate over the dataset 500 sims
simdata4 <- map_dfr(1:500, .f = dosims, fun = make_data4)
# make plots
tau4 <- sum(c(10/30, 10/30, 10/30)*(c(6, 3, 1)))
plot8 <- simdata4 %>% 
  ggplot(aes(x = estimate)) + 
  geom_density(fill = "#377EB8", alpha = 1/5) + 
  geom_vline(xintercept = tau4, linetype = "dashed", color = "#E41A1C", size = 1) + 
  ggtitle("Simulation 4") + 
  labs(subtitle = expression(paste("Staggered + Constant/Unequal ", tau))) +
  labs(x = "", y = "Density") + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
plot8

```
#1.2.2 Create DGP5:
similar to DGP2, but we will have 3 treatment periods instead of 1.
```{r data5, include = TRUE}
# Data 5 - Multiple Treatment Periods and Dynamic Equal Treatment Effects --------------

make_data5 <- function(...) {
  
  # Fixed Effects ------------------------------------------------
  # unit fixed effects
  unit <- tibble(
    unit = 1:600, 
    unit_fe = rnorm(600, 0, 0.5),
    # generate state
    state = sample(rep(1:30, 20), 600, replace = FALSE),
    # generate treatment groups
    group = case_when(
      state %in% 1:10 ~ 1999,
      state %in% 11:20 ~ 2008,
      state %in% 21:30 ~ 2017
    ),
    # avg yearly treatment effects by group
    hat_gamma = case_when(
      group == 1999 ~ .3,
      group == 2008 ~ .3,
      group == 2017 ~ .3
    )) %>%
    # generate unit specific yearly treatment effects 
    rowwise() %>% 
    mutate(gamma = rnorm(1, hat_gamma, .2), 0) %>% 
    ungroup()
  
  # year fixed effects 
  year <- tibble(
    year = 1990:2025,
    year_fe = rnorm(36, 0, 0.5))
  
  # full interaction of unit X year 
  crossing(unit, year) %>% 
    # make error term and get treatment indicators and treatment effects
    mutate(error = rnorm(nrow(.), 0, 0.5),
           treat = ifelse(year >= group, 1, 0),
           tau = ifelse(treat == 1, gamma, 0)) %>%
    # calculate the dep variable
    group_by(unit) %>% 
    mutate(cumtau = cumsum(tau)) %>% 
    mutate(dep_var = unit_fe + year_fe + cumtau + error)
}

# make data
data5 <- make_data5()
```
plot for data 5
```{r plot5, include = TRUE}
# plot 
plot9 <- data5 %>% 
  ggplot(aes(x = year, y = dep_var, group = unit)) +
  # unit specific lines
  geom_line(alpha = 1/10, color = "grey") + 
  # group specific averages
  geom_line(
    data = . %>% 
      group_by(group, year) %>% 
      summarize(dep_var = mean(dep_var)),
    aes(x = year, y = dep_var, group = factor(group),
        color = factor(group)), size = 1) + 
  labs(x = "", y = "", color = "Group") + 
  geom_vline(xintercept = 1998.5, color = "#A7473A",
             linetype = "dashed", size = 1) + 
  geom_vline(xintercept = 2007.5, color = "#4B5F6C" , 
             linetype = "dashed", size = 1) + 
  geom_vline(xintercept = 2016.5, color = "#51806a" , 
             linetype = "dashed", size = 1) + 
  scale_color_manual(values = c("#A7473A", "#4B5F6C", "#51806a")) + 
  scale_y_continuous(limits = c(-1, 10)) + 
  ggtitle("Simulation 5") + 
  labs(subtitle = expression(paste("Staggered + Dynamic/Equal ", tau))) +
  theme(legend.position = 'bottom',
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5), 
        plot.subtitle = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5, vjust = 0.5, angle = 360))
plot9
```
do 500 simulations, estimate ATT and plot for DGP5

```{r sim5, include= TRUE}
# do simulations, estimate ATT and plot ---------------------------------
# estimate over the dataset 500 sims
simdata5 <- map_dfr(1:500, .f = dosims, fun = make_data5)
# make plots 
tau5 <- # ATT for treated group in 1999
  (10/30) * mean(cumsum(rep(0.3, length(1999:2025)))) + 
  # ATT for treated group in 2008
  (10/30) * mean(cumsum(rep(0.3, length(2008:2025)))) + 
  # ATT for treated group in 2017
  (10/30) * mean(cumsum(rep(0.3, length(2017:2025))))
plot10 <- simdata5 %>% 
  ggplot(aes(x = estimate)) + 
  geom_density(fill = "#377EB8", alpha = 1/5) + 
  geom_vline(xintercept = tau5, linetype = "dashed", color = "#E41A1C", size = 1) + 
  geom_vline(xintercept = 0, linetype = "dashed", color = "black", size = 1) + 
  ggtitle("Simulation 5") + 
  labs(subtitle = expression(paste("Staggered + Dynamic/Equal ", tau))) +
  labs(y = "", x = expression(widehat(delta^'DD'))) + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
plot10
```
#1.2.3 Create DGP6: combine between DGP5 and DGP4, dynamic effect + different gamma.
```{r data6, include = TRUE}
# Data 6 - Multiple Treatment Periods and Dynamic Treatment Effects --------------
make_data6 <- function(...) {
  
  # Fixed Effects ------------------------------------------------
  # unit fixed effects
  unit <- tibble(
    unit = 1:600, 
    unit_fe = rnorm(600, 0, 0.5),
    # generate state
    state = sample(rep(1:30, 20), 600, replace = FALSE),
    # generate treatment groups
    group = case_when(
      state %in% 1:10 ~ 1999,
      state %in% 11:20 ~ 2008,
      state %in% 21:30 ~ 2017
    ),
    # avg yearly treatment effects by group
    hat_gamma = case_when(
      group == 1999 ~ .5,
      group == 2008 ~ .3,
      group == 2017 ~ .1
    )) %>%
    # generate unit specific yearly treatment effects 
    rowwise() %>% 
    mutate(gamma = rnorm(1, hat_gamma, .2), 0) %>% 
    ungroup()
  
  # year fixed effects 
  year <- tibble(
    year = 1990:2025,
    year_fe = rnorm(36, 0, 0.5))
  
  # full interaction of unit X year 
  crossing(unit, year) %>% 
    # make error term and get treatment indicators and treatment effects
    mutate(error = rnorm(nrow(.), 0, 0.5),
           treat = ifelse(year >= group, 1, 0),
           tau = ifelse(treat == 1, gamma, 0)) %>%
    # calculate the dep variable
    group_by(unit) %>% 
    mutate(cumtau = cumsum(tau)) %>% 
    mutate(dep_var = unit_fe + year_fe + cumtau + error)
}

# make data
data6 <- make_data6()
```

plot for DGP6
```{r plot6, include = TRUE}
plot11 <- data6 %>% 
  ggplot(aes(x = year, y = dep_var, group = unit)) +
  # unit specific lines
  geom_line(alpha = 1/10, color = "grey") + 
  # group specific averages
  geom_line(
    data = . %>% 
      group_by(group, year) %>% 
      summarize(dep_var = mean(dep_var)),
    aes(x = year, y = dep_var, group = factor(group),
        color = factor(group)), size = 1) + 
  labs(x = "", y = "", color = "Group") + 
  geom_vline(xintercept = 1998.5, color = "#A7473A",
             linetype = "dashed", size = 1) + 
  geom_vline(xintercept = 2007.5, color = "#4B5F6C" , 
             linetype = "dashed", size = 1) + 
  geom_vline(xintercept = 2016.5, color = "#51806a" , 
             linetype = "dashed", size = 1) + 
  scale_color_manual(values = c("#A7473A", "#4B5F6C", "#51806a")) + 
  scale_y_continuous(limits = c(-1, 20)) + 
  ggtitle("Simulation 6") + 
  labs(subtitle = expression(paste("Staggered + Dynamic/Unequal ", tau))) +
  theme(legend.position = 'bottom',
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5), 
        plot.subtitle = element_text(hjust = 0.5),
        axis.title.y = element_text(hjust = 0.5, vjust = 0.5, angle = 360))
plot11
```
```{r sim6, include= TRUE}
# do 500 simulations, estimate ATT and plot ---------------------------------
# make function to do this by data type 
dosims <- function(i, fun) {
  # make data from function
  dt <- fun()
  # estimate model and take what you need
  felm(dep_var ~ treat | unit + year | 0 | state, data = dt) %>% 
    broom::tidy(conf.int = TRUE) %>% 
    dplyr::select(estimate) %>% 
    dplyr::mutate(sim = i)
}

# estimate over the dataset 500 sims
simdata6 <- map_dfr(1:500, .f = dosims, fun = make_data6)
tau6 <- tau6 <- 
  # ATT for treated group in 1999
  (10/30) * mean(cumsum(rep(0.5, length(1999:2025)))) + 
  # ATT for treated group in 1998
  (10/30) * mean(cumsum(rep(0.3, length(2008:2025)))) + 
  # ATT for treated group in 2007
  (10/30) * mean(cumsum(rep(0.1, length(2017:2025))))
plot12 <- simdata6 %>% 
  ggplot(aes(x = estimate)) + 
  geom_density(fill = "#377EB8", alpha = 1/5) + 
  geom_vline(xintercept = tau6, linetype = "dashed", color = "#E41A1C", size = 1) + 
  geom_vline(xintercept = 0, linetype = "dashed", color = "black", size = 1) + 
  ggtitle("Simulation 6") + 
  labs(subtitle = expression(paste("Staggered + Dynamic/Unequal ", tau))) +
  labs(x = "", y = "") + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
plot12
```
#1.2.4 plot for 1.2
```{r plot7911, include= TRUE}
plot_dgp_456 <- plot7+ plot9+ plot11
plot_dgp_456
```

```{r plot81012, include = TRUE}
plot_TWFE_not_work <- plot8+ plot10+ plot12
plot_TWFE_not_work
```

##1.3 conclusion:
TWFE doesnt work well in heterogenenous TE. In DGP6, TWFE even gives negative estimates while in setting, all of the treatment effect are positive. it is because TWFE includes 'forbidden' comparisons, between early treated groups & later treated groups. 
(to find more insight, reader can find in paper of Goodman-Bacon 2020)
to solve this problem, CS & SA proposed different methods; only keeping clean comparisions, and making the result roburst. 


### Part2: CS & SA methods
CS & SA
##2.1 CS methods (briefly)
#2.1.1 key assumption: 
  Assummption 1: Random sampling. iid
  Assumption 2: conditional parallel trend based on a "Never-treated" group
  Assumption 3: conditional parallell trend based on a "Not-yet-treated" group
  Assumption 4: Irreversibility of Treatment
  Assumption 5: Overlap
  Assumption 6: No Anticipation.
#2.1.2 parameters of interest:  ATT(g,t), 'group-time average treatment effect', group - cohort g (first treated year g), time period t.
#2.1.3 How CS works
CS first estimate the full grid of cohort-by-time effects, then aggregate them into whichever summary you care about.(Dynamic event-time, group average, calendar-time average, overall ATT)
##2.2 SA methods (briefly)
#2.2.1 Assumptions
Assumption 1: Parallel trend in baseline
Assumption 2: No anticipatory
Assumption 3: Treatment Effect Homogeneity
#2.2.2 parameters of interest:
interaction-weighted (IW) event-time effect: for each relative time 
k (e.g., 2 years after treatment), they take a weighted average across cohorts of the cohort-specific effects at k, using only not-yet-treated units as comparisons. The weights are the cohorts’ shares among observations that contribute at that k (and are nonnegative and sum to 1).
##2.3 compare CS & SA (briefly)
#2.3.1 Framework
CS: focus on estimating ATT(g,t), build up an overall effect by aggregating these ATTs
SA: focus on event-study designs (relative time since treatment), corrects the TWFE event-study
regression so that each event-time coefficient is not contaminated by already-treated groups
#2.3.2 parallel trend assummption
CS:conditional parallel trend (not-yet treated & never treated)
SA:Parellel trend in baseline (stricter, only never-treated)
#2.3.3 treatment effect dynamic
CS: very general heterogeneity in treatment effects (by group and overtime)
SA: focus on dynamic treatmnet effects relative to treatment adoption
#2.3.4 No Anticipation
applied for both CS & SA

##2.4 simulation
To compare between CS & SA, and to prove that we can use these method in dynamic TE, we will use DGP6. 
#2.4.1 CS
```{r CS, include= TRUE}
# Callaway Sant'Anna -------------------------------------------------------------
# create a lead/lag indicators
data <- data6 %>% 
  # variable with relative year from treatment
  mutate(rel_year = year - group) %>% 
  # drop observations after 2016 bc all treated 
  filter(year <= 2016) %>% 
  dplyr::arrange(group, unit, year) %>% 
  ungroup()

# first get percentage contribution to each lead/lag indicator by treatment cohort for weights
# we will need this for the Abraham/Sun method, as well as the true treatment indicator
# calculate weights
weights <- data %>% 
  mutate(rel_year = year - group) %>% 
  # drop 2017 adopters
  filter(group != 2017) %>% 
  group_by(group, rel_year) %>% 
  count %>% 
  ungroup() %>% 
  group_by(rel_year) %>% 
  mutate(total = sum(n),
         perc = n / total) %>% 
  # keep just the variables we need
  select(rel_year, group, perc) %>% 
  ungroup() %>% 
  # get rid of negative numbers because glmt is weird
  mutate(rel_year2 = rel_year - min(rel_year)) %>% 
  rowwise() %>% 
  # add variable equal to coefficient from regression
  mutate(term = paste0("cohort_", group, "_", rel_year2)) %>% 
  ungroup()

# make a dataset with the theoretical values to merge in
true_effect <- weights %>% 
  # add in the multiples
  mutate(
    multiple = case_when(
      rel_year < 0 ~ 0,
      rel_year >= 0 ~ rel_year + 1),
    # add in the tau_g values 
    tau_g = case_when(
      group == 1999 ~ .5,
      group == 2008 ~ .3,
      group == 2017 ~ .1),
    # multiply the two 
    effect = multiple*tau_g) %>% 
  #collapse by  time period 
  group_by(rel_year) %>% 
  summarize(true_tau = weighted.mean(effect, w = perc)) %>% 
  # make the time variable for merging
  mutate(t = rel_year)

# create a first treated variable which is 0 for the 2017 cohort
data <- data %>% 
  mutate(first_treat = if_else(group == 2017, 0, group))

# run the CS algorithm
CS_out <- att_gt(yname = "dep_var", 
                 data = data,
                 gname = "first_treat",
                 idname = "unit", 
                 tname = "year", 
                 clustervars = "state",
                 bstrap = T, 
                 cband = T,
                 est_method = "reg",
                 control_group = "notyettreated",
                 print_details = F)

# get the event study estimates
es <- aggte(CS_out, type = "dynamic")

# plot
CS_ES <- tibble(
  t = es$egt,
  estimate = es$att.egt,
  se = es$se.egt,
  conf.low = estimate - 1.96*se,
  conf.high = estimate + 1.96*se
) %>% 
  #keep just years -5 to 5
  filter(t %>% between(-5, 5)) %>% 
  left_join(true_effect) %>% 
  # split the error bands by pre-post
  mutate(band_groups = case_when(
    t < -1 ~ "Pre",
    t >= 0 ~ "Post",
    t == -1 ~ ""
  )) %>%
  # plot
  ggplot(aes(x = t, y = estimate)) + 
  geom_line(aes(x = t, y = true_tau, color = "True Effect"), linetype = "dashed") + 
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, group = band_groups),
              color = "lightgrey", alpha = 1/4) + 
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = "Estimated Effect"), show.legend = FALSE) + 
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = -0.5, linetype = "dashed") + 
  scale_x_continuous(breaks = -5:5) + 
  labs(x = "Relative Time", y = expression(widehat(delta)['it'])) +
  scale_color_manual(values = c("#A7473A", "#4B5F6C")) + 
  ggtitle("Callaway & Sant'Anna") + 
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_text(angle = 360, hjust = 0.5, vjust = 0.5))
CS_ES
```
#2.4.2 SA
```{r SA, include = TRUE}
# Abraham and Sun -------------------------------------------------------------
## Make cohort-relative time dummies
dataAS <- data %>% 
  # replace rel_year = NA if last treated group
  mutate(rel_year2 = if_else(group == 2017, as.numeric(NA), rel_year),
         rel_year2 = rel_year2 - min(rel_year2, na.rm = TRUE)) %>% 
  # make a variable that is the interaction of group and relative year
  rowwise() %>% 
  mutate(cohort = if_else(group == 2017, as.character(NA), paste0(group, "_", rel_year2))) %>% 
  ungroup() %>% 
  dummy_cols(select_columns = "cohort", ignore_na = TRUE) %>% 
  mutate_at(vars(starts_with("cohort_")), ~replace_na(., 0))

# put the covariates into a vector form
# get the relative time indicators we use form the weights file
covs <- weights %>% filter(rel_year != -1 & rel_year > min(rel_year)) %>% pull(term)

# estimate the saturated model
fit <- felm(as.formula(paste("dep_var ~ ", paste(covs, collapse = "+"), "| unit + year | 0 | state")), 
            data = dataAS, exactDOF = TRUE)

# get the coefficients and make a dataset for plotting
coefs <- fit$coefficients %>%
  # add in coefficient name to tibble
  as_tibble(rownames = "term") %>% 
  # bring in weights
  left_join(., weights)

# get the relevant coefficients and weights into a string to get the linear combination
get_lincom <- function(ll) {
  # get just the coefficients for a specific lead lag
  cf2 <- coefs %>% filter(rel_year == ll)
  # paste the function that goes into the linear combination function
  F <- paste(paste(cf2$perc, cf2$term, sep = " * ", collapse = " + "), " = 0")
  # take linear combination and put into a data frame
  broom::tidy(
    confint(glht(fit, linfct = F)),
    conf.int = TRUE
  ) %>% mutate(rel_year = ll)
}

# run over all lead/lags
AS_plot <- map_df(c(-5:-2, 0:5), get_lincom) %>% 
  # add time variable
  mutate(t = c(-5:-2, 0:5))

#Plot the results
SA_ES <- AS_plot %>% 
  select(t, estimate, conf.low, conf.high) %>% 
  # add in data for year -1 (all zeros)
  bind_rows(tibble(t = -1, estimate = 0, 
                   conf.low = 0, conf.high = 0
  )) %>% 
  left_join(true_effect) %>% 
  # split the error bands by pre-post
  mutate(band_groups = case_when(
    t < -1 ~ "Pre",
    t >= 0 ~ "Post",
    t == -1 ~ ""
  )) %>%
  # plot
  ggplot(aes(x = t, y = estimate)) + 
  geom_line(aes(x = t, y = true_tau, color = "True Effect"), linetype = "dashed") + 
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, group = band_groups),
              color = "lightgrey", alpha = 1/4) + 
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = "Estimated Effect"), show.legend = FALSE) + 
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = -0.5, linetype = "dashed") + 
  scale_x_continuous(breaks = -5:5) + 
  labs(x = "Relative Time", y = expression(widehat(delta)['it'])) +
  scale_color_manual(values = c("#A7473A", "#4B5F6C")) + 
  ggtitle("Sun & Abraham") + 
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_text(angle = 360, hjust = 0.5, vjust = 0.5))
SA_ES
```



## 2.4.3 part 2 plots
```{r plotCSSA, include= TRUE}
plot_CS_SA <- CS_ES + SA_ES
plot_CS_SA
```

##conclusion:
SA & CS give a good estimate in this setting.


